 This thesis has been one of the most enjoyable and rewarding experiences that I have undertaken in my life. Whilst, at times, undertaking a PhD can feel a bit like a roller-coaster and present major challenges I have been lucky enough to have a large number of extremely supportive individuals around me. Without these people (and others!) this PhD would not have come to fruition.
 
 Firstly, I would like to express my sincerest gratitude to Dr Martin Meyer for supervising me on this project with tireless patience, dedication and mentoring. He has always given me freedom to dream and conduct new experiments whilst grounding me and keeping me on course. Above all, his excitement and enthusiasm towards new data and new questions is what has constantly inspired me and pushed me forward with this project. I could not have wished for a better supervisor. Besides my supervisor, I would like to thank my second supervisor Dr. Robert Hindges and my thesis committee members Dr. Juan Burrone and Dr. Isaac Bianco for their insightful comments and contributions.
 
 Thank you to all of the Meyer lab past and present: Dom, Dylan, Jade, Kostas, Nikolas, Matt, Paul, Rachel, Richard and Tom R. Working with all of you over these past few years has been a pleasure. You have all made the lab an enjoyable place to work and each one of you has contributed to the way I think as a scientist today. Special mentions go to both Giovanni Diana and Thomas Shallcross. Giovanni, I cannot describe how much I have learnt from you these past few years. You have changed the way that I think about and approach problems whilst becoming a friend for life. You have been an integral part of this project and I feel that the final results chapter was a chance for me to put into action many of the things that I have learnt from you. Tom, thank you for your support as a house mate and as a colleague. Our science chats in the pub and your support have helped me immensely.
 
 I would also like to thank friends from the CDN and beyond for your help and support over the years: Hannah, Suzie, Andy, Simon, Elin, Samir, Athena and many others.
 
 Last but not least I would like to show my sincerest gratitude to Alina, Mum, Dad, Alice, Gwil and Sophie. I have been a wreck these past few months, I would not have got through it without you. From the bottom of my heart thank you.
 